### 2016-11-01 paper/evaluation.tex
work in progress - added barplot from RQ2
Pass on eval - Subjects and Setup

We used the Github's Search API to fetch the top 1.000 projects in
Java with at least 100 stars. The number of stars indicates the
interest and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation for relevant projects
to conduct our study.\Jbc{Subject selection is currently OK but I will
use another way (eg Google BigQuery) to have access to more subjects.} To
scale the study, we considered only Maven projects with a
\emph{pom.xml} file located in the project's root directory. We could
also include support to other popular build manager systems but we
noticed that they are commonly related to a particular platform (\eg,
Gradle and Android) or the build process is based on user-defined
tasks (\eg, Ant).  \Comment{For each project, we detected the build
manager system based on the files located in the root directory (\eg,
\emph{pom.xml}) from the project in the following precedence: Maven,
Gradle, and Ant.} From the 1.000 downloaded projects, we selected the
154 projects that we were able to compile. \Jbc{Remember to update
those numbers (download + projects) after updating the subject
selection approach.}

@@

To run our experiments we used a Core i7-4790 (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running on Ubuntu 14.04 LTS Trusty Tahr
(64-bit version). We provided a \emph{Vagrantfile} to emulate our
hardware and software setup and dependency settings for replication.
All the source artifacts, including supporting scripts (\eg, the
script that test subjects and generates the raw data), and the full
list of projects are publicly available at \Fix{create gh-pages}.

@@

To evaluate the distribution of execution time, we calculated the cost
from 90\% of test cases ordered by execution time and compared the
resulting value to the total time.  We collected the elapsed time from
test cases for each generated report. Maven Surefire generates an XML
report with execution information (\eg, number of skipped tests and
elapsed time) per test suite \Jbc{Should I use the previous sentence
as a footnote or should I delete it?}. We noticed that some test
cases reported an elapsed time of zero: since the reported time is in
milliseconds, some tests may execute in a shorter time.

>>>>

We used the Github's Search API to fetch the top 1,000 Java projects
with at least 100 stars. The number of stars indicates the interest
and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study.\Jbc{Subject selection is currently OK
    but I will use another way (eg Google BigQuery) to have access to
more subjects.} For each project, we detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml)}, Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}). From the 1,000
downloaded projects (composed by \Fix{X} Maven, \Fix{Y} Gradle,
\Fix{W} Ant, and \Fix{W} unknown projects), we selected the 154 Maven
projects that we were able to compile\Jbc{Remember to update those
numbers (download + projects) after updating the subject selection
approach.}. We noticed that we are unable to compile other subjects
because other build systems are commonly related to a particular
platform (\eg, Gradle implied Android), the build process is based on
user-defined tasks (\eg, Ant), or the project has unsolved
dependencies.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Our evaluation scripts depends on \Fix{specify:
unix-based tools} to measure CPU usage and \emph{Python 3.4} (or
later). For replication, we provide all the source artifacts publicly
available at \Fix{create gh-pages}, including supporting scripts (\eg,
the script that test subjects and generates the raw data), the full
list of projects, and a \emph{Vagrantfile} to emulate our hardware and
software setup and dependency settings .

@@

To evaluate the distribution of execution time, we calculated the cost
from 90\% of test cases ordered by execution time and compared the
resulting value to the total time.  We collected the elapsed time from
test cases for each generated report. Maven Surefire generates an XML
report with execution information (\eg, number of skipped tests and
elapsed time) per test suite \Jbc{Should I use the previous sentence
as a footnote or should I delete it?}. We noticed that some test cases
reported an elapsed time of zero: since the reported time is in
milliseconds, some tests may execute in a shorter time. \Fix{..to be
continued...}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{figs/tcdistrib.pdf}
    \caption{\Fix{...}}
\end{figure}
